Analysis paper

### 2021-09-17 analysis/analysis-graveyard.Rmd
update code and plots

>>>>

--------------------------------------------------------------------------------
### alternative visualisation of forecasts
--> show underprediction, sharpness, overprediction in one plot

not yet done

```{r}
scores_over_time_plot_components <- function(scores) {

size = 1.8
width = 4

scores %>%
  ggplot(aes(x = forecast_date, 
             group = model, 
             color = model)) +

  geom_linerange(aes(ymin = -0.5*sharpness, ymax = 0.5 * sharpness, alpha = "Sharpness"), 
                 size = size,
                 alpha = 1,
                 position = position_dodge(width = width)) +

  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
                 size = size,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
                 size = size,
                 colour = "white",
                 size = size - 0.6,
                 alpha = 0.6,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
                 size = size,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
                 size = size,
                 colour = "white",
                 size = size - 0.6,
                 alpha = 0.6,
                 position = position_dodge(width = width)) + 
  theme_minimal() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                          max(forecast_dates$full_hub_period)))

}

# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
#   scores_over_time_plot_components() + 
#   scale_color_manual(values = colcases) + 
#   labs(y = "WIS rel. to baseline", x = "")

```{r}
# # calculate median and sd of the WIS -------------------------------------------
# 
# df <- eval_forecasts(
#   filtered_data[model %in% regular_models], 
#   metric = "interval_score",
#   summarise_by = c("model", "horizon", "target_type"), 
#   sd = TRUE, 
#   quantile = 0.5
# ) 
# 
# 
# df <- df[, .(model, horizon, target_type, 
#              `WIS - mean` = interval_score, 
#              `WIS - median` = interval_score_0.5, 
#              `WIS - sd` = interval_score_sd)] %>%
#     dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
# 
# setcolorder(df, c("target_type", "horizon", "model"))
# 
# 
# table <- df[order(target_type, horizon, model)] %>%
#   score_table()
# 
# save_kable(table, 
#            file = here("analysis", "plots", "table-wis-sd-median.png"))

```{r}
# calculate percentage differences in performance ------------------------------

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type")
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]

### 2021-09-17 analysis/analysis.Rmd
update code and plots

@@

  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.1,
                   alpha = 1,
                   position = position_dodge(width = dodgewidth)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    theme(panel.grid.major.x = element_blank()) +
    facet_wrap(~ location_target, scales = "free", ncol = 1) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits)
  return(p)
}

@@

  p <- scores %>%
    ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
    geom_line(aes(colour = model)) + 
    geom_point(aes(colour = model, shape = classification)) + 
    theme_minimal() + 
    facet_wrap( ~ location_target, ncol = 1, scales = "free") +
    theme(legend.position = "bottom") +
    theme(panel.grid.major.x = element_blank()) +
    scale_y_continuous(labels = comma) + # , 
                       # trans = log_trans()) + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits)
  return(p)
}

@@

    # truth plot for cases 
    truth_vs_forecast_cases <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "case") + 
      scale_color_manual(values = colcases) + 
      labs(y = "Forecasts and observed values", x = "")  + 
      theme(legend.position = "none") +
      guides(color = "none", shape = "none") + 
      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm"))

@@

# ensemble variants
models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
unfiltered_data[model %in% models] %>%
  forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
                       ensembles = TRUE)

--------------------------------------------------------------------------------
### alternative visualisation of forecasts

not yet done

```{r}
scores_over_time_plot_components <- function(scores) {

size = 1.8
width = 4

scores %>%
  ggplot(aes(x = forecast_date, 
             group = model, 
             color = model)) +

  geom_linerange(aes(ymin = -0.5*sharpness, ymax = 0.5 * sharpness, alpha = "Sharpness"), 
                 size = size,
                 alpha = 1,
                 position = position_dodge(width = width)) +

  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
                 size = size,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymax = -0.5 * sharpness, ymin = -0.5* sharpness - underprediction),
                 size = size,
                 colour = "white",
                 size = size - 0.6,
                 alpha = 0.6,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
                 size = size,
                 position = position_dodge(width = width)) + 
  geom_linerange(aes(ymin = 0.5 * sharpness, ymax = 0.5* sharpness + overprediction),
                 size = size,
                 colour = "white",
                 size = size - 0.6,
                 alpha = 0.6,
                 position = position_dodge(width = width)) + 
  theme_minimal() + 
  scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                          max(forecast_dates$full_hub_period)))

# scores_target_forecastdate[horizon == i & target_type == "case"] %>%
#   scores_over_time_plot_components() + 
#   scale_color_manual(values = colcases) + 
#   labs(y = "WIS rel. to baseline", x = "")

@@

  coverage <- eval_forecasts(
    data = data, 
    summarise_by = c("horizon", "model", "target_type", "range"), 
  )[range %in% c(50, 90), 
    .(model, target_type, coverage, range, horizon)] %>%
    dcast(formula = ... ~ range, value.var = "coverage")

  df <- eval_forecasts(
    data, 
    summarise_by = c("model", "horizon", "target_type"), 
    compute_relative_skill = FALSE,
    sd = TRUE, 
    quantiles = 0.5) %>%
    merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

  percentage_cols <- c("interval_score", "interval_score_0.5", 
                       "interval_score_sd", "sharpness", "underprediction", 
                       "overprediction", "aem")

  # no idea how to do that in data.table: 
  df <- df %>%
    dplyr::group_by(horizon, target_type) %>%
    dplyr::mutate_at(percentage_cols, ~ paste0(., " (", 
                                               round(100 * ./.[model == "Hub-ensemble"]), 
                                               "%)"))

@@

@@

```{r}
# # calculate median and sd of the WIS -------------------------------------------
# 
# df <- eval_forecasts(
#   filtered_data[model %in% regular_models], 
#   metric = "interval_score",
#   summarise_by = c("model", "horizon", "target_type"), 
#   sd = TRUE, 
#   quantile = 0.5
# ) 
# 
# 
# df <- df[, .(model, horizon, target_type, 
#              `WIS - mean` = interval_score, 
#              `WIS - median` = interval_score_0.5, 
#              `WIS - sd` = interval_score_sd)] %>%
#     dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))
# 
# setcolorder(df, c("target_type", "horizon", "model"))
# 
# 
# table <- df[order(target_type, horizon, model)] %>%
#   score_table()
# 
# save_kable(table, 
#            file = here("analysis", "plots", "table-wis-sd-median.png"))

```{r}
# calculate percentage differences in performance ------------------------------

df <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "horizon", "target_type")
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]

@@

  scale_fn <- function(x) {
    ifelse(x >= 5000,
           paste0(x / 1000, "k"), x)
  }

@@

  if (ranks) {
    df <- df %>%
      group_by(location_name, target_type, horizon, forecast_date) %>%
      arrange(location_name, target_type, horizon, forecast_date, interval_score) %>%
      mutate(!!x := rank(get(x)))

    xlabel <- "Rank in terms of WIS"
    dotsize = 0.1

  }
  + runif(length(get(x)), min = -0.1, max = 0.1)

@@

# function to make plot with mean of a given metric
plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
                        facet_formula, colour) {
  if (rel) {
    tmp <- tmp %>%
      arrange(target_type, !!sym(xvar)) %>%
      group_by(target_type, !!sym(xvar)) %>%
      mutate_at(y, ~ . / .[Model == "Hub-ensemble"])
  }

  tmp %>%
    ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
    geom_point(position = position_dodge(width = 0.1)) +
    geom_line(position = position_dodge(width = 0.1)) +
    facet_wrap(facet_formula, scales = "free_y") +
    theme_minimal() +
    theme(legend.position = "bottom") +
    scale_color_manual(values = colour)
}

# function for creating a component plot
component_plot <- function(scores, type, x = x, rel = relative,
                           facet_formula, vals = NULL) {

  if (type == "case" & is.null(vals)) {
    vals <- colcases
  } else if (type == "death" & is.null(vals)){
    vals <- coldeaths
  } else if (type == "case") {
    # filter out ensembles not needed
    scores <- scores %>%
      filter(!(Model %in% c("Hub-ensemble-with-all", "Hub-ensemble-with-convolution")))
    vals <- vals[-c(3, 4)]
  }

@@

  if (rel) {
    scores <- scores %>%
      arrange(!!sym(x), target_type, interval_score) %>%
      group_by(!!sym(x), target_type) %>%
      mutate_at("value", ~ . / interval_score[Model == "Hub-ensemble"])
  }

@@

score_helper <- function(data, summarise_by) {
  scores <- eval_forecasts(data, 
                           summarise_by = summarise_by, 
                           quantiles = 0.5, 
                           sd = TRUE) %>%
    filter(!(model %in% c("Hub-ensemble-with-all", 
                          "Hub-ensemble-with-convolution") & 
               target_type == "case"))

@@

  # mean performance
  p_mean <- 
    plot_helper(scores, y = "interval_score", rel = relative, 
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "mean WIS", x = NULL)

    # absolute error of performance
  p_aem <-
    plot_helper(scores, y = "aem", rel = relative, 
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "Absolute error", x = NULL)

  # sd of performance
  p_wis_sd <- 
    plot_helper(scores, y = "interval_score_sd", rel = relative, 
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "WIS - sd", x = NULL)

  # sharpness of performance
  p_sharpness <- 
    plot_helper(scores, y = "sharpness", rel = relative, 
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "Sharpness", x = NULL)

  # bias plot
  bias_limits <- max(abs(scores$bias)) * c(-1.1, 1.1) %>% 
    round(2)
  p_bias <- 
    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, 
                facet_formula = facet_formula) + 
    labs(y = "Bias", x = NULL) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    expand_limits(y=bias_limits)

  # plot with wis components
  component_case <- component_plot(scores, "case", x = x, vals = vals, 
                                   facet_formula = facet_formula, rel = relative)
  component_death <- component_plot(scores, "death", x = x, vals = vals, 
                                    facet_formula = facet_formula, rel = relative)
  components <- component_case + component_death

@@

  if (relative) {
    scores <- scores %>%
      arrange(target_type, range, !!sym(x)) %>%
      group_by(target_type, range, !!sym(x)) %>%
      mutate_at("coverage", ~ . - .[Model == "Hub-ensemble"])
  }

  p_cov50 <- scores %>%
    filter(range == c(50)) %>%
    plot_helper(y = "coverage", rel = FALSE, , facet_formula = facet_formula, 
                colour = vals) +
    labs(y = "Coverage - 50% PI") + 
    scale_y_continuous(labels = scales::percent)

  if (!relative) {
    p_cov50 <- p_cov50 + 
      expand_limits(y=c(0, 1)) + 
      geom_hline(yintercept = 0.5, linetype = "dashed") + 
      labs(y = "Diff. cov. - 50% PI", x = "") + 
      scale_y_continuous()
    }

  p_cov90 <-  scores %>%
    filter(range == c(90)) %>%
    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
                colour = vals) + 
    labs(y = "Coverage - 90% PI", x = "") + 
    scale_y_continuous(labels = scales::percent)

    if (!relative) {
      p_cov90 <- p_cov90 + 
        expand_limits(y=c(0, 1)) + 
        geom_hline(yintercept = 0.9, linetype = "dashed") + 
        labs(y = "Diff. cov. - 90% PI") + 
        scale_y_continuous()
    }

@@

>>>>

# helper function for labelling
scale_fn <- function(x) {
  ifelse(x >= 5000,
         paste0(x / 1000, "k"), x)
}

@@

  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = Model), 
                   size = 1.1,
                   alpha = 1,
                   position = position_dodge(width = dodgewidth)) + 
    geom_point(data = trend[target_type == ttype],
               aes(shape = Classification)) +
    geom_line(data = unfiltered_data[target_type == ttype & horizon == 2]) + 
    theme_minimal() + 
    theme(panel.grid.major.x = element_blank()) +
    facet_wrap(~ location_target, scales = "free", ncol = 1) + 
    theme(legend.position = "bottom") + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits) + 
      scale_y_continuous(labels = scale_fn)
  return(p)
}

@@

  p <- scores %>%
    ggplot(aes(x = as.Date(target_end_date), y = get(y))) + 
    geom_line(aes(colour = model)) + 
    geom_point(aes(colour = model, shape = classification)) + 
    theme_minimal() + 
    facet_wrap( ~ location_target, ncol = 1, scales = "free") +
    theme(legend.position = "bottom") +
    theme(panel.grid.major.x = element_blank()) +
    scale_y_continuous(labels = scale_fn) + # , 
                       # trans = log_trans()) + 
    scale_x_date(limits = c(min(limits), max(limits)), 
                 minor_breaks = limits) 
  return(p)
}

@@

    # truth plot for cases 
    truth_vs_forecast_cases <- df[grepl(i, target)] %>%
      truth_and_pred_plot(ttype = "case") + 
      scale_color_manual(values = colcases) + 
      labs(y = "Forecasts and observed values", x = "")  + 
      theme(legend.position = "none") +
      guides(color = "none", shape = "none") + 
      theme(plot.margin = unit(c(0.5,1.3,0.5,0.5), "cm")) + 
      scale_y_continuous(labels = scale_fn)

@@

# ensemble variants

# models <- c("Hub-ensemble-all", "Crowd forecast", "Hub-ensemble", "Renewal")
# unfiltered_data[model %in% models] %>%
#   forecasts_and_scores(plotname = "figure-forecasts-ensembles", 
#                        ensembles = TRUE)

@@

  coverage <- eval_forecasts(
    data = data, 
    summarise_by = c("horizon", "model", "target_type", "range"), 
  )[range %in% c(50, 90), 
    .(model, target_type, coverage, range, horizon)] %>%
    dcast(formula = ... ~ range, value.var = "coverage") %>%
    filter(!(model %in% c("Hub-ensemble-with-all", 
                          "Hub-ensemble-with-convolution", 
                          "Hub-ensemble-with-all-mean", 
                          "Hub-ensemble-with-convolution-mean") & 
               target_type == "case"))

  df <- eval_forecasts(
    data, 
    summarise_by = c("model", "horizon", "target_type"), 
    compute_relative_skill = FALSE,
    sd = TRUE) %>%
    filter(!(model %in% c("Hub-ensemble-with-all", 
                          "Hub-ensemble-with-convolution", 
                          "Hub-ensemble-with-all-mean", 
                          "Hub-ensemble-with-convolution-mean") & 
               target_type == "case")) %>%
    merge(coverage, all.x = TRUE, by = c("model", "horizon", "target_type"))

@@

  percentage_cols <- c("interval_score", 
                       "interval_score_sd", "sharpness", "underprediction", 
                       "overprediction", "aem")

  # no idea how to do that in data.table: 
  df <- df %>%
    dplyr::group_by(horizon, target_type) %>%
    dplyr::mutate_at(percentage_cols, 
                     ~ paste0(., " (", 
                              round(100 * ./.[model %in% c("Hub-ensemble", 
                                                           "Hub-ensemble-mean")]), 
                              "%)"))

@@

  setnames(df, old = c("interval_score_sd"), 
           new = c("WIS - sd"))

@@

@@

@@

  if (ranks) {
    df <- df %>%
      group_by(location_name, target_type, horizon, forecast_date) %>%
      arrange(location_name, target_type, horizon, forecast_date, interval_score) %>%
      mutate(!!x := rank(get(x))) %>%
      ungroup() 
    xlabel <- "Rank in terms of WIS"
    dotsize = 0.1

@@

# function to make plot with mean of a given metric
plot_helper <- function(tmp = scores, xvar = x, y, rel = relative, 
                        facet_formula, colour) {
  if (rel) {
    tmp <- tmp %>%
      arrange(target_type, !!sym(xvar)) %>%
      group_by(target_type, !!sym(xvar)) %>%
      mutate_at(y, ~ . / .[Model %in% c("Hub-ensemble", 
                                        "Hub-ensemble-mean")])
  }

  tmp %>%
    ggplot(aes_string(x = xvar, y = y, group = "Model", color = "Model")) +
    geom_point(position = position_dodge(width = 0.1)) +
    geom_line(position = position_dodge(width = 0.1)) +
    facet_wrap(facet_formula, scales = "free_y") +
    theme_minimal() +
    theme(legend.position = "bottom") +
    scale_color_manual(values = colour) + 
    scale_y_continuous(labels = scale_fn)
}

# function for creating a component plot
component_plot <- function(scores, type, colour_scheme, x = x, rel = relative,
                           facet_formula, vals = NULL) {

 if (colour_scheme == "ensemble") {
    # filter out ensembles not needed
    scores <- scores %>%
      filter(!(Model %in% c("Hub-ensemble-with-all", "Hub-ensemble-with-convolution")))
    vals <- vals[-c(3, 4)]
 } else if (type == "case") {
    vals <- vals[-1]
  }

@@

  if (rel) {
    scores <- scores %>%
      arrange(!!sym(x), target_type, interval_score) %>%
      group_by(!!sym(x), target_type) %>%
      mutate_at("value", ~ . / interval_score[Model %in% c("Hub-ensemble", 
                                                           "Hub-ensemble-mean")])
  }

@@

score_helper <- function(data, summarise_by) {
  scores <- eval_forecasts(data, 
                           summarise_by = summarise_by, 
                           quantiles = 0.5, 
                           sd = TRUE) %>%
    filter(!(model %in% c("Hub-ensemble-with-all", 
                          "Hub-ensemble-with-convolution", 
                          "Hub-ensemble-with-all-mean", 
                          "Hub-ensemble-with-convolution-mean") & 
               target_type == "case"))

@@

  # mean performance
  p_mean <- 
    plot_helper(scores, y = "interval_score", rel = relative, xvar = x, 
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "mean WIS", x = NULL)

    # absolute error of performance
  p_aem <-
    plot_helper(scores, y = "aem", rel = relative, xvar = x,
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "Absolute error", x = NULL)

  # sd of performance
  p_wis_sd <- 
    plot_helper(scores, y = "interval_score_sd", rel = relative, xvar = x,
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "WIS - sd", x = NULL)

  # sharpness of performance
  p_sharpness <- 
    plot_helper(scores, y = "sharpness", rel = relative, xvar = x,
                facet_formula = facet_formula, colour = vals) + 
    labs(y = "Sharpness", x = NULL)

  # bias plot
  bias_limits <- max(abs(scores$bias)) * c(-1.1, 1.1) %>% 
    round(2)
  p_bias <- 
    plot_helper(scores, y = "bias", rel = FALSE, colour = vals, xvar = x,
                facet_formula = facet_formula) + 
    labs(y = "Bias", x = NULL) +
    geom_hline(yintercept = 0, linetype = "dashed") +
    expand_limits(y=bias_limits)

  # plot with wis components
  component_case <- component_plot(scores, "case", x = x, vals = vals, 
                                   facet_formula = facet_formula, rel = relative, 
                                   colour_scheme = colour_scheme[1])
  component_death <- component_plot(scores, "death", x = x, vals = vals, 
                                    facet_formula = facet_formula, rel = relative, 
                                    colour_scheme = colour_scheme[1])
  components <- component_case + component_death

@@

  if (relative) {
    scores <- scores %>%
      arrange(target_type, range, !!sym(x)) %>%
      group_by(target_type, range, !!sym(x)) %>%
      mutate_at("coverage", ~ . - .[Model %in%  c("Hub-ensemble", 
                                                  "Hub-ensemble-mean")])
  }

  p_cov50 <- scores %>%
    filter(range == c(50)) %>%
    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
                colour = vals, xvar = x) +
    labs(y = "Diff. cov. - 50% PI", x = "") + 
    scale_y_continuous(labels = scales::percent)

  if (!relative) {
    p_cov50 <- p_cov50 + 
      expand_limits(y=c(0, 1)) + 
      labs(y = "Coverage - 50% PI", x = "") + 
      geom_hline(yintercept = 0.5, linetype = "dashed") + 
      scale_y_continuous(labels = scales::percent)
    }

  p_cov90 <-  scores %>%
    filter(range == c(90)) %>%
    plot_helper(y = "coverage", rel = FALSE, facet_formula = facet_formula, 
                xvar = x, colour = vals) + 
    labs(y = "Diff. cov. - 90% PI") + 
    scale_y_continuous(labels = scales::percent)

    if (!relative) {
      p_cov90 <- p_cov90 + 
        expand_limits(y=c(0, 1)) + 
        labs(y = "Coverage - 90% PI", x = "") + 
        geom_hline(yintercept = 0.9, linetype = "dashed") + 
        scale_y_continuous() + 
        scale_y_continuous(labels = scales::percent)
    }

@@

filtered_data[model %in% ensemble_models[grepl("mean", ensemble_models)]] %>%
  # filter(!(model == "Hub-ensemble-with-all" & target_type == "case")) %>%
  aggregate_performance(plotname = "aggregate-performance-rel-ensemble-mean", 
                        relative = TRUE, colour_scheme = "ensemble")
